---
title: '\textcolor{blue}{Homework 1}'
subtitle: "**21200842**"

format: 
  pdf
editor: visual
---

# \textcolor{blue}{Dataset}

Commit demonstration!

The `mtcars` dataset contains a column containing the fuel consumption `mpg` and 10 other columns detailing various aspects of the 32 cars. The simple dimensions of *32 rows* and *11 numeric columns* make this dataset easy to work with.

Further background can be found at: <https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars>

And a numeric summary is provided below:

```{r}
summary(mtcars)
```

# \textcolor{blue}{Plot}

As can be seen above, the summary statistics when just printed out look unwieldy and are hard to extract insights and relationships from at a glance. We will utilise a plot to provide a more aesthetic and insightful analysis of the data.

We focus on a scatterplot of miles per gallon vs horse power coloured by the number of cylinders. In this graph we can clearly see that a lower number of cylinders and a lower horse power correspond to higher miles per gallon. We also note that cars with lower weight (smaller circles) also tend to have higher miles per gallon.

Note also that we used the `ggthemes` package to provide a more aesthetically pleasing theme than the default `ggplot` theme.

```{r}
#| echo: false

library(ggthemes)
library(ggplot2)

# Load the  dataset
data("mtcars")

# Create a scatter plot of mpg vs hp coloured by cyl (number of cylinders) and sized by wt (weight)
ggplot(mtcars, aes(x=hp, y=mpg, color=factor(cyl), size=wt)) +
  geom_point(alpha=0.5) +
  theme_economist() +
  scale_fill_economist() +   labs(title="Scatter Plot of MPG vs Horsepower",
       x="Horsepower",
       y="Miles Per Gallon",
       color="Number of Cylinders",
       size="Weight (1000 lbs)") +
  theme(legend.position="right")
```
